Clustering Analysis of Mobility Data

### 2018-06-30 dokumentation/submission.tex
submission testdatagenerator

		\keywords{Clustering \and Rapidminer \and Cluster \and Data Mining} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction}
	\section{Preprocessing}
	\begin{itemize}
		\item max equal of 2038 for a strata 
		\item max equal of 595 per persona in strata
		\item vector calc.
	\end{itemize}
	\subsection{Vector}
	Instead of simple IDs for every person we expand the parsing by using a data encapsulating in a class called \texttt{Person}. This class stores the ID, the parameters defining a person %TODO: ref zu code basics
	, and all movements from that person.\\
	Then we are able to compute the following vector, with 848 entries, for further usage, that combines all movements of the person:
	\begin{align*}
	\underbrace{\#o_1, \dots, \#o_{413}, \#d_1, \dots, \#d_{413}}_{2\cdot 413} ,
	\underbrace{\mathit{AM}, \mathit{MD}, \mathit{PM}, \mathit{MN}}_{4}, 
	\underbrace{\#r_1, \dots, \#r_7}_{7}, \\
	\underbrace{\#\mathit{MoT}_1, \dots, \#\mathit{MoT}_7}_{7}, \underbrace{\mathit{SDest}, \mathit{SDist}, \mathit{G}, \mathit{A} ,\mathit{strata}, \mathit{strataGrouped}}_{6}
	\end{align*}
	with the following abbreviations ($1 \le i \le 413$, $1 \le j \le 7$):
	\begin{multicols}{2}
		\begin{itemize}
			\setlength{\itemindent}{.4cm}
			\item[$o_i$:]  the $i$-th origin data point
			\item[$d_i$:]  the $i$-th destination data point
			\item[$\mathit{AM}$:] movements at time stamp AM
			\item[$\mathit{MD}$:] movements at time stamp MD
			\item[$\mathit{PM}$:] movements at time stamp PM
			\item[$\mathit{MN}$:] movements at time stamp MN
			\item[$r_j$:] the $j$-th reason
			\item[$\mathit{MoT}_j$:] the $j$-th mean of transportation
			\item[$\mathit{SDest}$:] sum of all durations
			\item[$\mathit{SDist}$:] sum of all distances
			\item[$\mathit{G}$:] the gender
			\item[$\mathit{A}$:] the age
			\item[$strata$:] the strata (used for comparison)
			\item[$strataGrouped$:] the aggregated stratas
		\end{itemize}
	\end{multicols}
	\section{Predicting}

>>>>

		\keywords{Clustering \and Rapidminer \and Cluster \and Data Mining} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction}
	\section{Preprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line defining a \texttt{NotANumber}-exception and therefore gets neglected for further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments the script is able to create all test sets considered by our clustering and neural net approaches.\\
	%TODO: should this be within the paper or more in a ReadMe-file delivered with the script itself?
%	The possible flags and an explanation can be taken from \Cref{fig: testdatagenerator flags}.	
%	\begin{figure}[H]
%		\centering
%		\includegraphics[scale=0.5]{src/pic/testDataGenerator-h.PNG}
%		\caption{The possible arguments to the \texttt{testDataGenerator}}
%		\label{fig: testdatagenerator flags}
%	\end{figure}
	We observe the following distribution over the whole dataset:\\
	{\hspace*{2cm}\setlength\tabcolsep{.2cm}\begin{tabular}{c|ccccccc}
		strata &  1   &   2   &   3   &  4   &  5   &  6   & $\Sigma$ \\ \hline
		 abs   & 6963 & 52265 & 49404 & 8772 & 5536 & 2038 &  124978  \\
		  \%   & 5.57 & 41.82 & 39.53 & 7.02 & 4.43 & 1.63 &   100
	\end{tabular}}\\
	We observe that there is an upper bound on equal distribution through strata 6. It has at most 2038 individual elements.

	In addition to the original paper we compute the value \texttt{ID}, which is used to combine movements considered to be from the same person.
	We consider two movements to coincide on the underlying person, if and only if they are consecutive in the original dataset and have the same strata, age and gender.
	{\hspace*{2cm}\setlength\tabcolsep{.2cm}\begin{tabular}{c|ccccccc}
		strata &  1   &   2   &   3   &  4   &  5   &  6  & $\Sigma$ \\ \hline
		 abs   & 3153 & 23367 & 21418 & 3497 & 2083 & 595 &  54113   \\
		  \%   & 5.83 & 43.18 & 39.58 & 6.46 & 3.85 & 1.1 &   100
	\end{tabular}}\\
	So we also have through strata 6 an upper bound of 595 for equally distributed person vector data (see \Cref{subsec: person vector data}).

	\subsection{Vector}\label{subsec: person vector data}
	As stated before, instead of simple IDs for every person we expand the parsing by using a data encapsulating in a class called \texttt{Person}. This class stores the ID, the parameters defining a person %TODO: ref zu code basics
	, and all movements from that person.\\
	Then we are able to compute the following vector, with 848 entries, for further usage, that combines all movements of the person:
	\begin{align*}
	\underbrace{\#o_1, \dots, \#o_{413}, \#d_1, \dots, \#d_{413}}_{2\cdot 413} ,
	\underbrace{\mathit{AM}, \mathit{MD}, \mathit{PM}, \mathit{MN}}_{4}, 
	\underbrace{\#r_1, \dots, \#r_7}_{7}, \\
	\underbrace{\#\mathit{MoT}_1, \dots, \#\mathit{MoT}_7}_{7}, \underbrace{\mathit{SDest}, \mathit{SDist}, \mathit{G}, \mathit{A} ,\mathit{strata}, \mathit{strataGrouped}}_{6}
	\end{align*}
	with the following abbreviations ($1 \le i \le 413$, $1 \le j \le 7$):
	\begin{multicols}{2}
		\begin{itemize}
			\setlength{\itemindent}{.4cm}
			\item[$o_i$:]  the $i$-th origin data point
			\item[$d_i$:]  the $i$-th destination data point
			\item[$\mathit{AM}$:] movements at time stamp AM
			\item[$\mathit{MD}$:] movements at time stamp MD
			\item[$\mathit{PM}$:] movements at time stamp PM
			\item[$\mathit{MN}$:] movements at time stamp MN
			\item[$r_j$:] the $j$-th reason
			\item[$\mathit{MoT}_j$:] the $j$-th mean of transportation
			\item[$\mathit{SDest}$:] sum of all durations
			\item[$\mathit{SDist}$:] sum of all distances
			\item[$\mathit{G}$:] the gender
			\item[$\mathit{A}$:] the age
			\item[$strata$:] the strata (used for comparison)
			\item[$strataGrouped$:] the aggregated stratas
		\end{itemize}
	\end{multicols}
	\section{Predicting}
